%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[sfdefault]{carlito}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Faizan Ahmad} \\ \vspace{2pt}
    \Large \textit{Software Engineer} \\ \vspace{4pt}
    \small
    +92 300 1752535 $|$
    \href{mailto:faizan2002a@gmail.com}{\underline{faizan2002a@gmail.com}} $|$
    \href{https://www.linkedin.com/in/codefaizan}{\underline{LinkedIn}} $|$
    \href{https://github.com/codefaizan}{\underline{GitHub}} $|$
    \href{https://faizancodes.com}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{
Software Engineer with 2+ years of experience in mobile and backend development. Strong background in building cross-platform applications and scalable backend systems using Flutter, Django, and Node.js. Proven ability to optimize performance, integrate real-time features, and deliver production-ready solutions.
}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer}{July 2024 -- Present}
{Inara Technologies}{Islamabad}
\resumeItemListStart
\resumeItem{Developed and maintained mobile and backend applications using Flutter, Django, Node.js, and Firebase, improving scalability and system performance.}
\resumeItem{Implemented real-time chat using WebSockets, secure online payment integrations, and push notifications via Firebase Cloud Messaging (FCM).}
\resumeItem{Optimized API response times by approximately 20\% through query optimization and backend performance tuning.}
\resumeItemListEnd

\resumeSubheading
{Flutter Developer}{Jan 2024 -- July 2024}
{Astute Technologies}{Bahawalpur}
\resumeItemListStart
\resumeItem{Built and optimized mobile applications using Flutter and Firebase with real-time data synchronization.}
\resumeItem{Collaborated with backend and QA teams to deliver stable and user-friendly mobile solutions.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Cloud Storage Backend} $|$ \emph{Django, S3}}{}
\resumeItemListStart
\resumeItem{Built a secure and scalable backend for a cloud storage platform with authentication, account management, and storage usage tracking.}
\resumeItem{Designed REST APIs for file management with a focus on security, reliability, and performance for media-heavy workloads.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ETL \& Data Ingestion Platform} $|$ \emph{Django, ClickHouse}}{}
\resumeItemListStart
\resumeItem{Developed an ETL pipeline to ingest data from CSV, TXT, and Excel sources.}
\resumeItem{Implemented data cleaning, validation, and transformation workflows and loaded processed data into an analytical database.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{B2B E-commerce Platform Backend} $|$ \emph{Django}}{}
\resumeItemListStart
\resumeItem{Developed backend workflows enabling manufacturers to bid on product requirements submitted by retailers and admins.}
\resumeItem{Implemented order aggregation and dispatch logic for manufacturer fulfillment.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Gas Distributor Mobile App} $|$ \emph{Flutter, Node.js}}{}
\resumeItemListStart
\resumeItem{Built a mobile app for gas distributors to book gas, track deliveries in real time, and manage invoices and payments.}
\resumeItem{Replaced manual phone-based booking processes, significantly improving operational efficiency.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Soul of Agri} $|$ \emph{Flutter, Django}}{}
\resumeItemListStart
\resumeItem{Developed an agricultural advisory app enabling farmers to consult experts and receive crop-related guidance.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{EventHub} $|$ \emph{Flutter}}{}
\resumeItemListStart
\resumeItem{Built an event management app with real-time notifications using Firebase to improve organizer–attendee communication.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{The Islamia University of Bahawalpur}{Bahawalpur, Punjab}
{BS Software Engineering (CGPA: 3.80)}{Sept 2020 -- May 2024}

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{
\textbf{Technologies}{: Flutter, Django, Node.js, SQL, Firebase} \\
\textbf{Tools}{: Git, REST APIs, WebSockets, S3} \\
\textbf{Methodologies}{: Agile Development}
}}
\end{itemize}

%-----------EXTRACURRICULAR-----------
\section{Extracurricular}
\resumeSubHeadingListStart
\resumeSubheading
{Volunteer}{}
{Tech Destination of Pakistan Digital Conference}{}
\resumeItemListStart
\resumeItem{Organized and hosted training sessions aimed at equipping students with modern, in-demand technology skills.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
